### 2019-04-29 monograph/thesis/chapters/theorybase.tex
Renamed motivation.tex to theorybase.tex
On theorybase.tex created the new section for grammars and
other theory base tools.

% Is it possible to keep my translation together with original text?
% https://tex.stackexchange.com/questions/5076/is-it-possible-to-keep-my-translation-together-with-original-text
\chapter{\lang{Motivation}{Motivação}}

\section{\lang{What does coding is}{O que é programação}?}

@@

\section{\lang{Computer Assisted Programming}{Programação auxiliado pelo Computador}}

@@

>>>>

% Is it possible to keep my translation together with original text?
% https://tex.stackexchange.com/questions/5076/is-it-possible-to-keep-my-translation-together-with-original-text
\chapter{\lang{Theory base}{Fundamentação Teórica}}

\section{\lang{What does coding is}{Programação de computadores}}

@@

\subsection{\lang{Computer Assisted Programming}{Programação auxiliada}}

@@

\section{Gramáticas}

O que são Gramáticas?

\subsection{Expressões Regulares}

O que são Gramáticas?

\subsection{Gramáticas Livre de Contexto}

\subsection{Sintaxes de linguagens}

O que são sintaxes de linguagens?

\section{Formatadores de código}

Também conhecidos como embelezadores\footnote{do inglês:
Beautifiers} de código.

\section{Pretty-printing}

Depende do autor, ele é o mesmo que beautifying.
